---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MQMF

An R package for the book _Using R for Modelling and Quantitative Methods in Fisheries_ (2020).

To install the development version from [GitHub](https://github.com/) you can use:

```{r echo=TRUE, eval=FALSE}
if (!require(devtools)){install.packages("devtools")} 

devtools::install_github("https://github.com/haddonm/MQMF")
```

This new book is an evolution and adaptation my book _Modelling and Quantitative Methods in Fisheries_ (Haddon, 2011). It is designed to introduce materials needed to understand the use of R in fisheries and ecology. The book is not really for total beginners to R, but remains an introductory text in fisheries and population ecology because it covers a wide array of subjects and hence is limited in the depth in which each can be treated. Despite the breath of material, sufficient detail and worked examples are given that anyone should be able to make a good start with model fitting, characterizing uncertainty, and other basic fisheries model fitting. Subjects such as maximum likelihood, model fitting, and the estimation of uncertainty do receive relatively detailed attention. For example, there is a sufficient development around the use of MCMC that anyone should be able to develop a better understanding of its strengths and weaknesses. More advanced subjects such as age- and size-structured models are not included here as they are both very large subjects and are not suited to brief treatments.

This R package is almost ready to be submitted to CRAN, and currently has no errors, no warnings, and no notes, and passes the tests used R CMD check --as-cran and those used by the rhub package.

Malcolm Haddon

February 20 2020


Haddon, M. (2011) _Modelling and Quantitative Methods in Fisheries_. 2nd Ed. CRC/Chapman & Hall. 449p.

Haddon, M. (2020) _Using R for Modelling and Quantitative Methods in Fisheries_. CRC/Chapman & Hall. In Press


